Untrusted B2B Collaboration using the Blockchain

### 2018-07-10 paper/paper.tex
More notes, more gitignore

%TODO reference original blockchain paper
Blockchain technology is used in cryptocurrencies, most notably Bitcoin \cite{nakamoto2008bitcoin}.
The use in cryptocurrency has laid the foundation for a number of decentralized application besides financial ones.
Ethereum \cite{wood2014ethereum} is a cryptocurrency that also builds on blockchain technologies and allows users to execute code in the form of \emph{smart contracts}.
Smart contracts are Turing complete code artifacts, that can be deployed on the blockchain and have an interface that is callable by users. 
They can receive and send money, store information locally and emit events on the blockchain ledger.
When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
Contracts deplete gas for each operation and return excess gas back to the user.
This ensures that contracts are not running for an unlimited amount of time and that computations on the blockchain are expensive in order to avoid unnecessary operations being performed on-chain.
%TODO short text on the paper which shows smart contract examples

\subsection{Prior Work on Business Processes on the Blockchain}
%summarize untrusted paper
%summarize Caterpillar
%acknowledge their Work
%display the shortcomings
A work by Weber et. al \cite{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
They use a smart contract that all parties of a business process communicate with.
They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.

>>>>

%TODO reference original blockchain paper
Blockchain technology is used in cryptocurrencies, most notably Bitcoin \cite{nakamoto2008bitcoin}.
The use in cryptocurrency has laid the foundation for a number of decentralized application besides financial ones.
Ethereum \cite{wood2014ethereum} is a cryptocurrency that also builds on blockchain technologies and allows users to execute code in the form of \emph{smart contracts}.
Smart contracts are Turing complete code artifacts, that can be deployed on the blockchain and have an interface that is callable by users. 
They can receive and send money, store information locally and emit events on the blockchain ledger.
When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
Contracts deplete gas for each operation and return excess gas back to the user.
This ensures that contracts are not running for an unlimited amount of time and that computations on the blockchain are expensive in order to avoid unnecessary operations being performed on-chain.
%TODO short text on the paper which shows smart contract examples
%TODO short text on solidity

\subsection{Prior Work on Business Processes on the Blockchain}
In \cite{weber2016untrusted}, a first approach of monitoring and coordinating business process interactions across organizations on the blockchain was presented.
Using a smart contract as a central \emph{monitor} or \emph{mediator} of the communication, a form of inter-process orchestration is implemented.
They describe a contract architecture, where a factory contract is responsible for deploying instance contracts for each process instance.
They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
In order to achieve BPMN-to-Solidity compilation, they describe translation rules to transform BPMN elements to Solidity code.
%TODO highlight lack of access right explanation and problem of central contract?

%we build on:
%factories \& instances
%registering users to roles
%triggers
%the model they used (originally from Fdhila et al)

%we don\'t:
%do bpmn solidity translation
%use one central contract instance

%summarize Caterpillar
%acknowledge their Work
%display the shortcomings
\cite{lopez2017caterpillar} presents an open-source implementation of an Ethereum-based Business Process Management System.
It implements BPMN-to-Solidity compilation and thereby tracks the state of process executions on the blockchain.
Processes can be started and executed via a user interface, which calls the generated Solidity code in the background.

%describes components and architecture of engine
%automatic bpmn solidity translation
%no choreographies / lanes supported, all tasks / transitions are managed on-chain through process %contract
